### 2015-02-27 icfp15-servo/browsers.tex
ms2ger's changes

A URL identifies a resource to load.
This resource usually consists of HTML, which is then parsed and typically turned into a Document Object
Model (DOM) tree.
From a programming languages standpoint, there are several interesting aspects of the parser design
for HTML.
First, though the specification allows the browser to abort on a parse error\footnote{\url{https://html.spec.whatwg.org/multipage/syntax.html#parsing}},
in practice browsers follow the recovery algorithms described in that specification precisely so that
even ill-formed HTML will be handled in an interoperable way across all browsers..
Second, due to the presence of the \lstinline[language=HTML]{<script>} tag, the token stream can be modified
during operation.
For example, the below example that injects an open tag for the header and comment blocks works in all modern browsers.
\begin{lstlisting}[language=HTML]
<html>
  <script>
  document.write(``<h'');
  </script>1>
  This is a h1 title

@@

After constructing the DOM and determining the set of styles defined in the Cascading Style Sheets (CSS) that has
been loaded, those styles are applied to the DOM and a new tree that represents the elements is created.
This process can create many more elements than previously existed in the DOM --- for example, when a list item is
styled to have an associated counter glyph.

>>>>

A URL identifies a resource to load.
This resource usually consists of HTML, which is then parsed and typically turned into a Document Object
Model (DOM) tree.
From a programming languages standpoint, there are several interesting aspects of the parser design
for HTML.
First, though the specification allows the browser to abort on a parse error\footnote{\url{https://html.spec.whatwg.org/multipage/#parsing}},
in practice browsers follow the recovery algorithms described in that specification precisely so that
even ill-formed HTML will be handled in an interoperable way across all browsers..
Second, due to the presence of the \lstinline[language=HTML]{<script>} tag, the token stream can be modified
during operation.
For example, the below example that injects an open tag for the header and comment blocks works in all modern browsers.
\begin{lstlisting}[language=HTML]
<html>
  <script>
  document.write(``<h'');
  </script>1>
  This is a h1 title

@@

After constructing the DOM and determining the set of styles defined in the Cascading Style Sheets (CSS) that has
been loaded, those styles are applied to the DOM and a new flow tree that represents the elements is created.
This process can create many more flows than previously existed in the DOM --- for example, when a list item is
styled to have an associated counter glyph.
